---
title: "Linear Regression"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyverse)
library(dplyr)
library(data.table)
library(nnet)
library(broom)
```

Loading in the data:
```{r, include=FALSE}
neighbor_data = 
  read_excel("./Data/temp_data.xlsx", sheet = 2) %>%
  janitor::clean_names() %>% 
  select(-c(x1)) %>% 
    mutate(ceb = as.numeric(ceb),
           median_age = as.numeric(median_age),
           percent_female = as.numeric(percent_female),
           fuel_used_for_cooking_percent_wood_dung = as.numeric(fuel_used_for_cooking_percent_wood_dung),
           percent_public_source = as.numeric(percent_public_source),
           percent_private_toilet = as.numeric(percent_private_toilet),
           percent_employed = as.numeric(percent_employed),
           percent_without_hs_education = as.numeric(percent_without_hs_education),
           percent_marital_status = as.numeric(percent_marital_status),
           percent_caste = as.numeric(percent_caste)
         ) 

outcome_data = 
  read_excel("./Data/temp_data.xlsx", sheet = 3) %>%
  separate(sbp, into = c("sbp", "sbp_sd")) %>% 
  separate(dbp, into = c("dbp", "dbp_sd")) %>% 
  separate(  bmi, into = c("bmi", "bmi_sd")) %>% 
  janitor::clean_names() %>% 
  mutate(ceb = as.numeric(ceb),
         fbg = as.numeric(fbg),
         fbg_sd = as.numeric(fbg_sd),
         sbp = as.numeric(sbp),
         sbp_sd = as.numeric(sbp_sd),
         dbp = as.numeric(dbp),
         dbp_sd = as.numeric(dbp_sd),
         bmi = as.numeric(bmi),
         bmi_sd = as.numeric(bmi_sd),
         hypertension = as.numeric(hypertension),
         diabetes = as.numeric(diabetes)
         ) %>% 
  select(ceb, fbg, sbp, dbp, bmi)

total= merge(neighbor_data, outcome_data, by="ceb")
```
Model 1: Fasting Blood Glucose

Crude:
```{r, echo=FALSE}
fbg_crude=
  lm(fbg ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste, data=total)

summary(fbg_crude)
summary(fbg_crude)$coef
coef(fbg_crude)
fitted.values(fbg_crude)

fbg_crude %>% 
  broom::glance()

fbg_crude %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_fbg_crude_metrics =
  augment(fbg_crude) 

model_fbg_crude_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(fbg_crude)
```

Age as a confounder:
```{r, echo=FALSE}
fbg_age=
  lm(fbg ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + median_age, data=total)

summary(fbg_age)
summary(fbg_age)$coef
coef(fbg_age)
fitted.values(fbg_age)

fbg_age %>% 
  broom::glance()

fbg_age %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_fbg_age_metrics =
  augment(fbg_age) 

model_fbg_age_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(fbg_age)
```

Gender as a confounder:

```{r, echo=FALSE}
fbg_gender=
  lm(fbg ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + percent_female, data=total)

summary(fbg_gender)
summary(fbg_gender)$coef
coef(fbg_gender)
fitted.values(fbg_gender)

fbg_gender %>% 
  broom::glance()

fbg_gender %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_fbg_gender_metrics =
  augment(fbg_gender) 

model_fbg_gender_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(fbg_gender)
```

Marital status as a confounder:

```{r, echo=FALSE}
fbg_marital=
  lm(fbg ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + percent_marital_status, data=total)

summary(fbg_marital)
summary(fbg_marital)$coef
coef(fbg_marital)
fitted.values(fbg_marital)

fbg_marital %>% 
  broom::glance()

fbg_marital %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_fbg_marital_metrics =
  augment(fbg_marital) 

model_fbg_marital_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(fbg_marital)
```

Full model:
```{r, echo=FALSE}
fbg_full=
  lm(fbg ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + median_age + percent_female + percent_marital_status, data=total)

summary(fbg_full)
summary(fbg_full)$coef
coef(fbg_full)
fitted.values(fbg_full)

fbg_full %>% 
  broom::glance()

fbg_full %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_fbg_full_metrics =
  augment(fbg_full) 

model_fbg_full_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(fbg_full)
```

Model 2: BMI

Crude:
```{r, echo=FALSE}
bmi_crude=
  lm(bmi ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste, data=total)

summary(bmi_crude)
summary(bmi_crude)$coef
coef(bmi_crude)
fitted.values(bmi_crude)

bmi_crude %>% 
  broom::glance()

bmi_crude %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_bmi_crude_metrics =
  augment(bmi_crude) 

model_bmi_crude_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(bmi_crude)
```

Age as a confounder:
```{r, echo=FALSE}
bmi_age=
  lm(bmi ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + median_age, data=total)

summary(bmi_age)
summary(bmi_age)$coef
coef(bmi_age)
fitted.values(bmi_age)

bmi_age %>% 
  broom::glance()

bmi_age %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_bmi_age_metrics =
  augment(bmi_age) 

model_bmi_age_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(bmi_age)
```

Gender as a confounder:

```{r, echo=FALSE}
bmi_gender=
  lm(bmi ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + percent_female, data=total)

summary(bmi_gender)
summary(bmi_gender)$coef
coef(bmi_gender)
fitted.values(bmi_gender)

bmi_gender %>% 
  broom::glance()

bmi_gender %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_bmi_gender_metrics =
  augment(bmi_gender) 

model_bmi_gender_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(bmi_gender)
```

Marital status as a confounder:

```{r, echo=FALSE}
bmi_marital=
  lm(bmi ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + percent_marital_status, data=total)

summary(bmi_marital)
summary(bmi_marital)$coef
coef(bmi_marital)
fitted.values(bmi_marital)

bmi_marital %>% 
  broom::glance()

bmi_marital %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_bmi_marital_metrics =
  augment(bmi_marital) 

model_bmi_marital_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(bmi_marital)
```

Full model:
```{r, echo=FALSE}
bmi_full=
  lm(bmi ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + median_age + percent_female + percent_marital_status, data=total)

summary(bmi_full)
summary(bmi_full)$coef
coef(bmi_full)
fitted.values(bmi_full)

bmi_full %>% 
  broom::glance()

bmi_full %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_bmi_full_metrics =
  augment(bmi_full) 

model_bmi_full_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(bmi_full)
```

Model 3: Systolic Blood Pressure

Crude:
```{r, echo=FALSE}
sbp_crude=
  lm(sbp ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste, data=total)

summary(sbp_crude)
summary(sbp_crude)$coef
coef(sbp_crude)
fitted.values(sbp_crude)

sbp_crude %>% 
  broom::glance()

sbp_crude %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_sbp_crude_metrics =
  augment(sbp_crude) 

model_sbp_crude_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(sbp_crude)
```

Age as a confounder:
```{r, echo=FALSE}
sbp_age=
  lm(sbp ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + median_age, data=total)

summary(sbp_age)
summary(sbp_age)$coef
coef(sbp_age)
fitted.values(sbp_age)

sbp_age %>% 
  broom::glance()

sbp_age %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_sbp_age_metrics =
  augment(sbp_age) 

model_sbp_age_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(sbp_age)
```

Gender as a confounder:

```{r, echo=FALSE}
sbp_gender=
  lm(sbp ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + percent_female, data=total)

summary(sbp_gender)
summary(sbp_gender)$coef
coef(sbp_gender)
fitted.values(sbp_gender)

sbp_gender %>% 
  broom::glance()

sbp_gender %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_sbp_gender_metrics =
  augment(sbp_gender) 

model_sbp_gender_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(sbp_gender)
```

Marital status as a confounder:

```{r, echo=FALSE}
sbp_marital=
  lm(sbp ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + percent_marital_status, data=total)

summary(sbp_marital)
summary(sbp_marital)$coef
coef(sbp_marital)
fitted.values(sbp_marital)

sbp_marital %>% 
  broom::glance()

sbp_marital %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_sbp_marital_metrics =
  augment(sbp_marital) 

model_sbp_marital_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(sbp_marital)
```

Full model:
```{r, echo=FALSE}
sbp_full=
  lm(sbp ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + median_age + percent_female + percent_marital_status, data=total)

summary(sbp_full)
summary(sbp_full)$coef
coef(sbp_full)
fitted.values(sbp_full)

sbp_full %>% 
  broom::glance()

sbp_full %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_sbp_full_metrics =
  augment(sbp_full) 

model_sbp_full_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(sbp_full)
```

Model 4: Diastolic Blood Pressure

Crude:
```{r, echo=FALSE}
dbp_crude=
  lm(dbp ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste, data=total)

summary(dbp_crude)
summary(dbp_crude)$coef
coef(dbp_crude)
fitted.values(dbp_crude)

dbp_crude %>% 
  broom::glance()

dbp_crude %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_dbp_crude_metrics =
  augment(dbp_crude) 

model_dbp_crude_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(dbp_crude)
```

Age as a confounder:
```{r, echo=FALSE}
dbp_age=
  lm(dbp ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + median_age, data=total)

summary(dbp_age)
summary(dbp_age)$coef
coef(dbp_age)
fitted.values(dbp_age)

dbp_age %>% 
  broom::glance()

dbp_age %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_dbp_age_metrics =
  augment(dbp_age) 

model_dbp_age_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(dbp_age)
```

Gender as a confounder:

```{r, echo=FALSE}
dbp_gender=
  lm(dbp ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + percent_female, data=total)

summary(dbp_gender)
summary(dbp_gender)$coef
coef(dbp_gender)
fitted.values(dbp_gender)

dbp_gender %>% 
  broom::glance()

dbp_gender %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_dbp_gender_metrics =
  augment(dbp_gender) 

model_dbp_gender_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(dbp_gender)
```

Marital status as a confounder:

```{r, echo=FALSE}
dbp_marital=
  lm(dbp ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + percent_marital_status, data=total)

summary(dbp_marital)
summary(dbp_marital)$coef
coef(dbp_marital)
fitted.values(dbp_marital)

dbp_marital %>% 
  broom::glance()

dbp_marital %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_dbp_marital_metrics =
  augment(dbp_marital) 

model_dbp_marital_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(dbp_marital)
```

Full model:
```{r, echo=FALSE}
dbp_full=
  lm(dbp ~ fuel_used_for_cooking_percent_wood_dung + percent_public_source + percent_private_toilet + percent_employed + percent_without_hs_education + percent_caste + median_age + percent_female + percent_marital_status, data=total)

summary(dbp_full)
summary(dbp_full)$coef
coef(dbp_full)
fitted.values(dbp_full)

dbp_full %>% 
  broom::glance()

dbp_full %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)

model_dbp_full_metrics =
  augment(dbp_full) 

model_dbp_full_metrics %>% 
  knitr::kable()

par(mfrow = c(2, 2))
plot(dbp_full)
```
